\cvsection{Work Experience}

\begin{cventries}

  \cventry
    {Soderling Laboratory, Duke University} % mono-upper
    {Graduate Research Assistant} % bold-left
    {Fall 2016 - May 2021} % italics-right
    {Department of Neurobiology} % Blue-right
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Development of novel spatial proteomics analysis pipeline for clustering
	      and statistical inference in multiplex spatial proteomics.}
      \item {Application and development of CRISPR-based methods for genetic
	      depletion and tagging of endogenous proteins leading to founding
	      of CasTag BioSciences.}
      \item {Performed synaptosome subcellular fractionation to assess
	      synaptic changes in multiple mouse models of human brain disorders.}
      \item {Experience working with numerous model organisms including immortalized cell lines,
	      bacteria, yeast, and mice.}
      \item {Appliction and analysis of BioID-based proximity proteomics for identification
	      of subcellular specific compartments.}
      \item {Normalization and analysis of RNA transcriptomics and
	      protein proteomics datasets.}
      \item {Recipient of a Ruth L. Kirschstein National Research Service Award
	      Fellowship (NRSA F31) to study a protein of unknown function and
	      the mechanisms by which its loss causes a rare epilepsy disorder.}
      \end{cvitems}
    }

  \cventry
    {Soderling Laboratory, Duke University}
    {Research Technician}
    {May 2014 - May 2016} 
    {Department of Cell Biology} 
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
      \item {Protein co-immunoprecipitation and proximity proteomics for
	      identification of protein-protein interactions and revealing
	      protein interactomes \textit{in vivo}--first application of BioID
	      \textit{in vivo} and proteome of inhibitory post-synapse published
	      in \textit{Science}.}
      \item {Performed immunoblotting, immunostaining, and cell and tissue
	      culture for assessing protein expression and localization
	      \textit{in vitro} and \textit{in vivo}.}
      \item {Molecular cloning and generation of adeno-associated virus for transgene expression
	      \textit{in vivo}.} 
      \item {Maintained mouse colony with >30 strains of mice; performed mouse
	      surgery, husbandry, genotyping, and analysis of mouse behavior.}
      \end{cvitems}
    }

\end{cventries}
