\cvsection{Publications}


\begin{cventries}

% ----
  \cventry
    {Co-first Author} % Role
	{Courtland \textit{et al.,}} % Title
	{eLife} % Journal
	{2021} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {\textit{Genetic Disruption of WASHC4 Drives Endo-lysosomal
	      Dysfunction and Cognitive-Movement Impairments in Mice and Human.}
	      Jamie Courtland, \textbf{Tyler Bradshaw}, Greg Waitt,
	      Erik Soderblom, Tricia Ho, Anna Rajab, Ricardo Vancini,
	      Il Hwan Kim, Scott Soderling.
	      \href{https://www.biorxiv.org/content/10.1101/2020.08.06.239517v1}{biorxiv}}
      \end{cvitems}
    }

% ----
  \cventry
    {Co-second Author} % Role
	{Uezu \textit{et al.,}} % Title
	{Science} % Location
	{2016} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {\textit{Identification of an Elaborate Complex Mediating Postsynaptic Inhibition.}
	      Akiyoshi Uezu, Daniel J. Kanak, \textbf{Tyler W.A. Bradshaw}, Erik
	      J. Soderblom, Christina M. Catavero, Alain C. Burette, Richard J. Weinberg, and
	      Scott H. Soderling. \href{https://science.sciencemag.org/node/683771.full}{Science}
	      2016 Sep 9; 353(6304): 1123–1129. \textbf{DOI:} 10.1126/science.aag0821}
      \end{cvitems}
    }

% ----
  \cventry
    {Co-Author} % Role
	{Gao \textit{et al.,}} % Title
	{Neuron} % Location
	{2018} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {\textit{Plug-and-Play Protein Modification Using Homology-Independent Universal Genome Engineering.}
	      Yudong Gao, Erin Hisey, \textbf{Tyler W.A. Bradshaw}, Eda Erata, Walter E. Brown,
	      Jamie L. Courtland, Akiyoshi Uezu, Yu Xiang, Yarui Diao, and Scott H. Soderling. 
	      \href{https://www.cell.com/neuron/fulltext/S0896-6273(19)30523-9}{Neuron}
	      2018 July 1; S0896-6273(19)30523-9. \textbf{DOI:} 10.1016/j.neuron.2019.05.047}
      \end{cvitems}
    }

% ----
  \cventry
    {Co-Author} % Role
	{Uezu \textit{et al.,}} % Title
	{eLife} % Location
	{2019} % Date(s)
    {
      \begin{cvitems} % Description(s)
      \item {\textit{Essential role for InSyn1 in dystroglycan complex integrity
	      and cognitive behaviors in mice.} Akiyoshi Uezu, Erin Hisey,
	      Yoshihiko Kobayashi, Yudong Gao, \textbf{Tyler W.A. Bradshaw},
	      Patrick Devlin, Ramona Rodriguiz, Purushothama Rao Tata, and Scott
	      Soderling. \href{https://elifesciences.org/articles/50712}{eLife}
	      2019 Dec 12;8:e50712. \textbf{doi:} 10.7554/eLife.50712.}
      \end{cvitems}
    }
    
\end{cventries}
